---
title: "Descriptive Tables"
author: "Regan Johnston"
date: "`r Sys.Date()`"
output:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
```

##creating the tables 1
```{r}
tbl_1 = sample %>% 
  gtsummary::tbl_summary(include = c(srh, 
                            edatt, 
                            faminc, 
                            age, 
                            married, 
                            kidsinhh),
              type = list(faminc ~ 'continuous',
                          kidsinhh ~ 'continuous'),
  by        = sex,
              
              statistic = list(all_continuous()  ~ "{mean} ({sd})",
                               all_dichotomous() ~ "0.{p}",
                               all_categorical() ~ "0.{p}"),
              
              digits    = list(all_continuous()  ~ 2,
                               all_categorical() ~ 0)) %>% 
  
gtsummary::modify_header(update = list(label  ~ '**Variables**',
                              stat_1 ~ '**Male ({n})**', 
                              stat_2 ~ '**Female({n})**')) %>% 
  
gtsummary::modify_footnote(update = c(stat_1, stat_2) ~ 
                  'Mean and standard deviations provided for continuous 
                  variables. Proportions provided for categorical variables') %>% 
  
gtsummary::modify_caption('**TABLE 1. DESCRIPTIVE STATISTICS (N = 20153)**') %>%

  gtsummary::bold_labels()


  # Prints Table 1 as HTML
tbl_1 %>% as_gt()

```

# CREATING TABLE 1: DESCRIPTIVE STATISTICS

  # Creating and Storing Table: tbl_1
tbl_1 <- sample %>% 
  tbl_summary(include   = c(srh, 
                            srh_m, 
                            edatt, 
                            faminc, 
                            age, 
                            married, 
                            kidsinhh, 
                            racialmin),
              type = list(faminc   ~ 'continuous',
                          kidsinhh ~ 'continuous'),
              
              by        = sex,
              
              statistic = list(all_continuous()  ~ "{mean} ({sd})",
                               all_dichotomous() ~ "0.{p}",
                               all_categorical() ~ "0.{p}"),
              
              digits    = list(all_continuous()  ~ 2,
                               all_categorical() ~ 0)) %>% 
  
  modify_header(update = list(label  ~ '**Variables**',
                              stat_1 ~ '**Male ({n})**', 
                              stat_2 ~ '**Female({n})**')) %>% 
  
  modify_footnote(update = c(stat_1, stat_2) ~ 
                  'Mean and standard deviations provided for continuous 
                  variables. Proportions provided for categorical variables') %>% 
  
  modify_caption('**TABLE 1. DESCRIPTIVE STATISTICS (N = 19755)**') %>% 
  
  bold_labels()


  # Prints Table 1 as HTML
tbl_1 %>% as_gt()




#second table
```{r, results ='asis'}

# CREATING TABLE 2: OLS REGRESSIONS OF SRH AND HOUSEWORK

  # Linear Model of Self-Rated Mental Health
    # y ~ x1 + x2 + x3 ... , data = )
ols_srh <- lm(srh ~ edatt * sex + 
                    age +
                    married +         
                    faminc +        
                    kidsinhh,       
                data = sample,
                weights = wght_per)

  # Creating SRH Table based on Linear Model
model_srh <- 
tbl_regression(ols_srh) %>% 
  gtsummary::modify_header(update = list(label = '**Variables**',
                              estimate  = '***b***',
                              std.error = '***se***',
                              p.value   = '**p-value**')) %>% 
  add_significance_stars()


  # Linear Model of Self-Reported Finance
    # y ~ x1 + x2 + x3 ... , data = )
ols_finance <- lm(finance ~ edatt * sex + 
                       age +
                       married +         
                       faminc +        
                       kidsinhh,      
                 data = sample,
                 weights = wght_per)

  # Creating Finance Table based on Linear Model
model_finance <- 
  tbl_regression(ols_finance) %>% 
  gtsummary::modify_header(update = list(label = '**Variables**',
                              estimate  = '***b***',
                              std.error = '***se***',
                              p.value   = '**p-value**')) %>% 
  add_significance_stars()


  # Merging Tables to Create and Store Table 2: tbl_2
tbl_2 =
tbl_merge(list(model_srh, model_finance),
          tab_spanner = c('**Self-Rated Mental Health**', 
                          '**Self-Rated Finacial Responsibilities**')) %>% 
          modify_caption('**TABLE 2 (N = 20153)**') %>% 
          modify_footnote(update = c('p.value_1', 'p.value_2') ~ 'Significant p-values in bold.')

    # Prints Table 2 in HTML
tbl_2 %>% as_gt()
  
```
